### 2015-02-20 fundamentals/impl.tex
missing of

Version control preserves the development history, or \emph{provenance}, of
source code files. \Cyclus uses a well-established \emph{distributed version
control} tool called git \cite{software_freedom_conservancy_git_2014} for this
purpose.  Distributed version control allows every
user to have complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
One feature that git performs exceptionally well is \emph{branching}.
Branches are distinct pathways in the history that diverge from a mainline source
tree and then may be \emph{merged} back into the mainline. Multiple simultaneous
branches may exist at all points in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an
accompanying message. Thus
it is possible for \Cyclus to accurately replay the entirety of who did what to the
code when.

@@

Since these steps are performed for all incoming code, it is easy for the
\Cyclus core team to determine whether or not an individual pull request
actually works. This helps identify build and test problems prior to
broken code being allowed into the develop branch. \gls{CI} is a necessary
but not sufficient addition to the \Cyclus \gls{QA}
system: it keeps bad code out \Cyclus. However, \Cyclus will always
require human eyes and hands to let good code in.

>>>>

Version control preserves the development history, or \emph{provenance}, of
source code files. \Cyclus uses a well-established \emph{distributed version
control} tool called git \cite{software_freedom_conservancy_git_2014} for this
purpose.  Distributed version control allows every
user to have complete local copy of the \emph{repository} (the version control
term for the collection of all possible histories).
One feature that git performs exceptionally well is \emph{branching}.
Branches are distinct pathways in the history that diverge from a mainline source
tree and then may be \emph{merged} back in. Multiple simultaneous
branches may exist at all points in time. Every change to the code is recorded
in the history, along with metadata such as the author, a timestamp, and an
accompanying message. Thus,
it is possible for \Cyclus to accurately replay the entirety of who did what to the
code when.

@@

Since these steps are performed for all incoming code, it is easyi for the
\Cyclus core team to determine whether or not an individual pull request
actually works. This helps identify build and test problems prior to
broken code being allowed into the develop branch. \gls{CI} is a necessary
but not sufficient addition to the \Cyclus \gls{QA}
system: it keeps bad code out of \Cyclus. However, \Cyclus will always
require human eyes and hands to let good code in.
